\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.4 in,top=0.4in,right=0.4 in,bottom=0.4in]{geometry} % Document margins
\usepackage{multicol}

\usepackage{tikz}
\newcommand{\ExternalLink}{%
    \tikz[x=1.2ex, y=1.2ex, baseline=-0.05ex]{% 
        \begin{scope}[x=1ex, y=1ex]
            \clip (-0.1,-0.1) 
                --++ (-0, 1.2) 
                --++ (0.6, 0) 
                --++ (0, -0.6) 
                --++ (0.6, 0) 
                --++ (0, -1);
            \path[draw, 
                line width = 0.5, 
                rounded corners=0.5] 
                (0,0) rectangle (1,1);
        \end{scope}
        \path[draw, line width = 0.5] (0.5, 0.5) 
            -- (1, 1);
        \path[draw, line width = 0.5] (0.6, 1) 
            -- (1, 1) -- (1, 0.6);
        }
    }
    
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}} 
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Ayandeep Dutta} % Your name
% You can merge both of these into a single line, if you do not have a website.
\address{(+91) 9434586150 \\ Hooghly, West Bengal} 
\address{\href{mailto:ayandeepd1@gmail.com}{ayandeepd1@gmail.com}   \\ 
\href{https://www.linkedin.com/in/ayandeepd1/}{linkedin/ayandeepd1} \\ 
\href{https://github.com/ayandeepd1}{github/ayandeepd1}
} % 

\begin{document}

%----------------------------------------------------------------------------------------
%	OBJECTIVE
%----------------------------------------------------------------------------------------
%

%\begin{rSection}{OBJECTIVE}

%{An innovative developer, interested in Embedded System, IOT, and Robotics and having moderate understanding of cloud and web api integration. Takes  interest in innovating systems and integrating robust technologies. A team player and enthusiastic to learn about new technology in consumer electronics, industrial automation and chip design and manufacture in India.}

%random text
%---------PCB design


%\end{rSection}
%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf Kalinga Institute of Industrial Technology}, Bhubaneshwar  \hfill {October 2021 – September 2025}\\
Btech 3rd year in Electronics and Computer Science

{\bf Vivekananda Academy}, West Bengal   \hfill {2021} \\ 12th pass CBSE

{\bf Don Bosco Bandel}, West Bengal  \hfill {2019}\\10th pass ICSE


\end{rSection}

%----------------------------------------------------------------------------------------
% TECHINICAL STRENGTHS	
%----------------------------------------------------------------------------------------

\begin{rSection}{Achievements}
\begin{itemize}
    \item	\textbf{Qualified} {\href{https://drive.google.com/file/d/19b68QH18MYZ5I7WiuYsy_8Nba_L_EQp0/view?usp=sharing}{\ExternalLink}ISRO UROC Space Robotics Challenge 2024}
    \item	\textbf{Finalist} {\href{https://drive.google.com/file/d/1W6QaTl4ACOmYrGS4B4s7wk6i5bp0PqeC/view?usp=sharing}{\ExternalLink}Flipkart Grid 5.0 Robotics Challenge 2024 at IIT Madras}
    \item 	\textbf{Qualified and Attended} {\href{https://drive.google.com/file/d/1W2yoG2iqVNsBk0JT7XLYXPjSYqRyBf_P/view?usp=sharing}{\ExternalLink}Oppo Inspiration Challenge 2023 at Bangkok}
    \item	\textbf{Second Position}{\href{https://drive.google.com/file/d/1m1xp8iycSMY3Qm0ifF1HrywmXu0pscT0/view?usp=drive_link}{\ExternalLink} in IEEE Vegathon 2023 by CDAC at IIT Guwahati}
    \item 	\textbf{First Position}{\href{https://drive.google.com/file/d/1Uw5ZY3Zb5v_DlN1RiNWilV_b84GE2wOb/view?usp=sharing}{\ExternalLink} India Innovates 2023 at IIT Kharagpur}
    
\end{itemize}
\end{rSection} 

\begin{rSection}{PROJECTS}
\vspace{-1.25em}
\item \textbf{Voice Integrated Home Automation} {\href{https://github.com/ayandeepd1/iot_esp_automation}{\ExternalLink} \\
-An esp8266 wifi enabled IoT Node.
-Analog Voice amplification using amplifier. 
-Voice recording using interrupt functionality.
-Voice Recognition using Google assistant api.
-Python based Backend hosted on AWS EC2.
-Relay control and Notification playback.
-User Interface Frontend hosted on 000webhost.com.
}

\item \textbf{Gesture Recognition Glove} {\href{https://drive.google.com/file/d/1x3BAbsTNXpl_hvw0puoTsikSn7FdMiW4/view}{\ExternalLink}\\
-A glove like device to recognize hand gestures using AI.
-Play preassigned voice feedback to known gestures.
-Based on stm32f103 and esp32c3pico.
-Uses ADC and IMU for movements of fingers and hands.
-BLE connectivity with android app.
-FreeRtos scheduling is used to manage tasks.
-Battery powered device.
}

\item \textbf{Displaying BMP image on NeoPixel Matrices} {\href{https://github.com/ayandeepd1/image_mapping_on_neopixel_matrix}{\ExternalLink}\\
-Three 30x30 Neopixel led panels in snakelines configuration.
-Generated a series of bmp images using JINX software.
-Converted bmp image files into 2D array of RGB pixels.
-Split pixel array and stored as binary files on SD card.
-Esp32 reads SD card and display image in each Neopixel panel. }

\item \textbf{Plant Growth with Environment Monitoring and Control System} {\href{https://github.com/ayandeepd1/IllumiFarmer}{\ExternalLink} \\
A system to contain and enhance growth rate of plants in a close environment by subjecting to specific wavelength light and maintaining  optimal climate and soil conditions.
}
\end{rSection} 


\begin{rSection}{SKILLS}
    \begin{multicols}{3}
    \begin{itemize}
        \item Embedded System design        
        \item Embedded C
        \item Arduino                                       
        \item Stm32 Bare Metal
        \item ESP32 Free Rtos 
        \item Linux
        \item C++
        \item Python
        \item MySQL
    \end{itemize}
    \end{multicols}
\end{rSection}
\begin{rSection}{POSITIONS OF RESPONSIBILITY}
\begin{itemize}
    \item	\textbf{ASST. COORDINATOR} {KIIT Robotics Society}
    \item	\textbf{RND LEAD} {KIIT Robotics Society}
\end{itemize}
\end{rSection}
%--------------------------------------------------`--------------------------------------
%\begin{rSection}{Extra-Curricular Activities} 
%\begin{itemize}
%    \item 	\textbf{KIIT ROBOTICS SOCIETY} {\href{https://www.linkedin.com/company/kiit-robotics-society-bbsr/}{\ExternalLink}\\
%    Community Member. }
%    \item	\textbf{RC UAVs, Drones}
%\end{itemize}
%\end{rSection}

%----------------------------------------------------------------------------------------

\end{document}
